---
title: "HSMR public dashboard - Google analytics report"
author: "Public Health Scotland"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
---
  
  ```{r TODO, include = FALSE}
# Add tables/downloadable data?
# Anything else to add to report? (geography?)
# Schedule it to run every month

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F) # prevents code to be shown in report

#Packages
library(dplyr)
library(plotly)
library(knitr)
```

```{r env}
data_folder <- "/conf/quality_indicators/hsmr/quarter_cycle/Dashboard/google_analytics/"

sessions <- readRDS(paste0(data_folder, "sessions.rds"))
tabvisits <- readRDS(paste0(data_folder, "tabvisits.rds"))
tabvisits_year <- readRDS(paste0(data_folder, "tabvisits_yearly.rds"))
device <- readRDS(paste0(data_folder, "device.rds"))
source <- readRDS(paste0(data_folder, "source.rds"))
pages <- readRDS(paste0(data_folder, "pages.rds"))

```

```{r plot_parameter}

# Style of x and y axis
xaxis_plots <- list(title = FALSE, tickfont = list(size=14), 
                    titlefont = list(size=14),
                    showline = TRUE, fixedrange=TRUE,
                    rangeslider = list(type = "date", thickness = 0.075
                                       # Without this, range will change when adding/removing markers
                    ))

yaxis_plots <- list(title = "Number of visits", rangemode="tozero", 
                    fixedrange=TRUE, size = 4,
                    tickfont = list(size=14), titlefont = list(size=14))

# Buttons to remove
bttn_remove <-  list('select2d', 'lasso2d', 'zoomIn2d', 'zoomOut2d',
                     'autoScale2d',   'toggleSpikelines',  'hoverCompareCartesian',
                     'hoverClosestCartesian', 'zoom2d', 'pan2d', 'resetScale2d') 

# For annotation
zoom_hover_text =
  "Drag the markers at either end of<br>the bar to view specific time periods"

# We need an annotation to show user how to use the rangeslider
zoom_annotation =
  list(text = "Drag to zoom", borderpad = 2,
       hovertext = zoom_hover_text,
       showarrow = TRUE, ax = 0, ay = 18,
       x = 0, xref = "paper", xanchor = "left",
       y = -0.35, yref = "paper", yanchor = "middle")

# Annotation to mark when 
monthly_annotation =
  list(text = "Drag to zoom", borderpad = 2,
       hovertext = zoom_hover_text,
       showarrow = TRUE, ax = 0, ay = 18,
       x = 0, xref = "paper", xanchor = "left",
       y = -0.35, yref = "paper", yanchor = "middle")

###############################################.
# Palettes 
pal_tabs <- c('#000000', '#4da6ff','#ffa64d')

```

This reports shows the visits to the HSMR public dashboard and each one
of their tabs. Data only available from mid June 22 for overall visits and from the end of July 22 for tab visits.

## Number of sessions over the last year

```{r overall}
kable(device)
```

## Overall visits to the dashboard

```{r sessions}
#Tooltip for the sessions chart
tooltip_sess <- c(paste0("Week ending: ", format(sessions$week_ending, "%d %B %Y"), "<br>",
                         "Visits: ", sessions$count))

# Plot for the overall visits
plot_ly(sessions) %>% 
  add_lines(x = ~week_ending, y = ~count,
            text=tooltip_sess, hoverinfo="text") %>% 
  layout(yaxis = yaxis_plots, xaxis = xaxis_plots,
         margin = list(b = 80, t = 5, r = 25), # to avoid labels getting cut off
         annotations = zoom_annotation) %>%    
  config(displaylogo = F, displayModeBar = TRUE, 
         modeBarButtonsToRemove = bttn_remove ) # leaving only save plot button

```

## Visits to each tab

### Visits in last year
```{r taboverallvisits}
#Tooltip for the sessions chart
tooltip_tabvisits <- c(paste0("Section: ", tabvisits_year$tabname, "<br>",
                              "Visits: ", tabvisits_year$count))

# Adjusting some of the axis formatting
yaxis_bar <- xaxis_plots
yaxis_bar[["rangeslider"]] <- NULL
yaxis_bar[["categoryorder"]] <- "array"
yaxis_bar[["categoryarray"]] <- tabvisits_year %>% arrange(count) %>% pull(tabname)

# Plot for the overall visits
plot_ly(tabvisits_year) %>% 
  add_bars(y = ~tabname, x = ~count, textposition="none",
           text=tooltip_tabvisits, hoverinfo="text") %>% 
  layout(yaxis = yaxis_bar, xaxis = yaxis_plots) %>% 
  # leaving only save plot button
  config(displaylogo = F, displayModeBar = TRUE, 
         modeBarButtonsToRemove = bttn_remove )

```

### Visits per wek

```{r tabweekvisits}
#Plot function for tabs data

  tooltip_plot <- c(paste0(tabvisits$tabname, "<br>",
                           "Week ending: ", format(tabvisits$week_ending, "%d %B %Y"), "<br>",
                           "Visits: ", tabvisits$count))
  
  plot_ly(tabvisits, x = ~week_ending) %>% 
    add_trace(y = ~count, color = ~tabname,
              colors = pal_tabs,
              type = "scatter", mode = "lines+markers",
              text=tooltip_plot, hoverinfo="text") %>% 
    #Layout
    layout(yaxis = yaxis_plots, xaxis = xaxis_plots,
           margin = list(b = 80, t = 5, r = 25), # to avoid labels getting cut off
           annotations = zoom_annotation) %>% 
    # leaving only save plot button
    config(displaylogo = F, displayModeBar = TRUE, 
           modeBarButtonsToRemove = bttn_remove )

```

## Average session length

```{r ave_sess}


#Tooltip for the sessions chart
tooltip_sess <- c(paste0("Week ending: ", format(sessions$week_ending, "%d %B %Y"), "<br>",
                         "Average minutes: ", sessions$session_ave))

# Plot for the overall visits
plot_ly(sessions) %>% 
  add_lines(x = ~week_ending, y = ~session_ave,
            text=tooltip_sess, hoverinfo="text") %>% 
  layout(yaxis = list(yaxis_plots, title = "Average minutes spent in website"), 
         xaxis = xaxis_plots,
         margin = list(b = 80, t = 5, r = 25), # to avoid labels getting cut off
         annotations = zoom_annotation) %>% 
  # leaving only save plot button
  config(displaylogo = F, displayModeBar = TRUE, 
         modeBarButtonsToRemove = bttn_remove )

```

## Sources of visits over the last year

```{r source}
kable(source)
```

## Pages visited

```{r pages}
kable(pages)
```

